MSHS COVID-19 Vaccinations

### 2021-04-07 Evening-Huddle-Stats.Rmd
Update reference file.
Update reference file for afternoon huddle analysis.

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-04-01.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-04-01.xlsx"),
                           sheet = "Pod Mappings Simple")

@@

  this_weeks_dates <- format(
    sort(this_week_prior_days %>%
           select(ApptDate))$ApptDate, "%m/%d/%y")

>>>>

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-04-07.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-04-07.xlsx"),
                           sheet = "Pod Mappings Simple")

@@

  this_weeks_dates <- format(
    sort((this_week_prior_days %>%
           select(ApptDate))$ApptDate), "%m/%d/%y")
